---
title: "Fisher's Test-Simulation"
author: "Zihui Wang"
date: "2022-10-13"
output: 
  pdf_document: default
---

```{r, include=F}
library(ggplot2)
```

*The data was generated from a randomized experiment carried out around 1970 in Southern Florida to evaluate cloud seeding.*  
*On each of 52 days that were suitable for cloud seeding, a random mechanism was used to decide whether to seed or not.*  
*A plane flew through the clouds each suitable day (both seeding and non-seeding days).*  
*The experimenter set up the plane to inject or not depending on the random outcome.*  
*The plane’s pilot did not know whether the seeding mechanism was loaded to inject or not.*  
*Precipitation was measured as total rain volume (in acre-feet) resulting from the clouds in the 24 hours following the plane’s run.*  
```{r}
cloudseed<-read.csv("/Users/wangzihui/Downloads/cloudseed.csv",header=T)
pooled_data<-c(cloudseed$seeded,cloudseed$unseeded)
```

```{r}
#Simulating to get p-value testing Fisher’s sharp null hypothesis of no treatment effect
set.seed(29)

nrep<-1000
simulation_T<-NULL

for(i in 1:nrep){
  random<-sample(1:52,26,replace=F)
  simulation_T[i]<-abs(mean(pooled_data[random])-mean(pooled_data[-random]))
}

sample_T<-abs(mean(cloudseed$seeded)-mean(cloudseed$unseeded))
pval<-length(simulation_T[simulation_T>=sample_T])/nrep
pval<-round(pval,digits=3)

#Plot the histogram
ggplot()+
  geom_histogram(aes(x=simulation_T,y=after_stat(density)),binwidth=20,fill="blue",color="blue",alpha=0.5,size=0.1)+
  geom_segment(aes(x=sample_T,xend=sample_T,y=0.0006,yend=0.003))+
  geom_text(aes(x=sample_T,y=0.0032,label=paste("T observed=",sample_T)),size=4,inherit.aes = FALSE)+
  geom_text(aes(x=300,y=0.005,label=paste("p-value=",pval)),size=4.5,inherit.aes = FALSE)+
  theme_bw()
```
  
```{r}
#Testing whether  variability rather than mean amount of the rainfall increased
set.seed(29)

simulation_T2<-NULL

for(i in 1:nrep){
  random<-sample(1:52,26,replace=F)
  simulation_T2[i]<-var(pooled_data[random])/var(pooled_data[-random])
}

sample_T2<-var(cloudseed$seeded)/var(cloudseed$unseeded)
sample_T2<-round(sample_T2,digits=3)
pval2<-length(simulation_T2[simulation_T2>=sample_T2])/nrep
pval2<-round(pval2,digits=3)

#Plot the histogram
ggplot()+
  geom_histogram(aes(x=simulation_T2,y=after_stat(density)),binwidth=0.5,fill="blue",color="blue",alpha=0.5,size=0.1)+
  geom_segment(aes(x=sample_T2,xend=sample_T2,y=0.1,yend=0.65))+
  geom_text(aes(x=1.5*sample_T2,y=0.75,label=paste("T2 observed=",sample_T2)),size=4,inherit.aes = FALSE)+
  geom_text(aes(x=25,y=0.9,label=paste("p-value=",pval2)),size=4.5,inherit.aes = FALSE)+
  theme_bw()
```
  
```{r}
#Regard the impact of cloud as multiplicative rather than additive
set.seed(29)

simulation_T3<-NULL

for(i in 1:nrep){
  random<-sample(1:52,26,replace=F)
  simulation_T3[i]<-abs(mean(log(pooled_data[random]))-mean(log(pooled_data[-random])))
}

sample_T3<-abs(mean(log(cloudseed$seeded))-mean(log(cloudseed$unseeded)))
sample_T3<-round(sample_T3,digits=3)
pval3<-length(simulation_T3[simulation_T3>=sample_T3])/nrep
pval3<-round(pval3,digits=3)

#plot the histogram
ggplot()+
  geom_histogram(aes(x=simulation_T3,y=after_stat(density)),binwidth=0.1,fill="blue",color="blue",alpha=0.5,size=0.1)+
  geom_segment(aes(x=sample_T3,xend=sample_T3,y=0.2,yend=1))+
  geom_text(aes(x=1.05,y=1.2,label=paste("T3 observed=",sample_T3)),size=4,inherit.aes = FALSE)+
  geom_text(aes(x=0.7,y=1.5,label=paste("p-value=",pval3)),size=4.5,inherit.aes = FALSE)+
  theme_bw()
```